Tableau Project 2
====
**Group members: Fabiana Latorre, Oliver Benton Javier, Ernesto Canales, and Nikolaj Plagborg-Moller.**  

Our dataset can be found at 'http://catalog.data.gov/dataset/new-york-city-leading-causes-of-death-ce97f'.

We load the data-table into a variable named 'df' and display a subset of the data. To show data tables, we often use the 'head' function instead of tbl_df, since tbl_df sometimes does not display the important columns of a table.
  
```{r}
source('../01 SQL Crosstabs/Fetching_data.R', echo=TRUE)
```

We use a sub-query to sum the death counts in groups of year and death cause. The causes of death are then ranked according to their count for each year. The resulting table is displayed below along with a crosstab that lists the top five most frequent death causes for each year. We limited it to the top five, so that the resulting crosstab fits in this document.

```{r}
source('../01 SQL Crosstabs/Rank.R', echo=TRUE)
```

```{r}
source('../01 SQL Crosstabs/Nth_Value.R', echo=TRUE)
```

```{r}
source('../01 SQL Crosstabs/Cume_Dist.R', echo=TRUE)
```